CYO Project Report - Brazilian Ecommerce

### 2021-07-13 finalReport.Rmd
created final model

```{r Final movel validation, echo = FALSE}
validation_dataset <- validation_dataset %>% select(-seller_id,-handed_over_to_carrier_date,-shipping_limit_date)

predictions <- predict(final_model,validation_dataset %>% select(-number_of_hours))

RMSE((validation_dataset %>% pull(number_of_hours) ),predictions)
# 194.6748 for mtry=25, ntree=500
```

>>>>

```{r Final model validation, echo = FALSE}
predictions <- predict(final_model,validation_dataset %>% select(-number_of_hours))

RMSE((validation_dataset %>% pull(number_of_hours) ),predictions)
# 190.184 for mtry=15, ntree=500
```
